### 2022-07-31 paper/Chapters/Chapter05.tex
update eval

The approaches are trained on dataset "synthetic-50-5" as mentioned in Chapter \ref{ch:04} with 3000 scenes. The screen size is $ 128\times 128 $ in height and width. The corresponding vertex matrix has dimension $ 128\times 128\times3 $, light map has dimension $ 128\times 128 \times 3 $, image has dimension $ 128\times 128 \times 1 $.  The training pipeline use batch size $ 8 $,  Adam optimizer (\cite{adam}), learning rate of  $ 1\times10^{-3} $, learning schedule [8,1000], learning decay factor 0.5. 
The model is trained with PyTorch 1.10.0a0, CUDA 11.4.1, GPU with single NVIDIA GEFORCE RTX 3090.

\section{GCNN model evaluation}
The GCNN model is the base model of the whole thesis. The architecture is described in \ref{sec:gcnn}. We use a single GCNN to estimate the surface normal based on geometry information. It uses vertex map as input to estimate the corresponding tangent surface normal map. 
%% gcnn-eval
\begin{figure}[H]
	\centering
	\begin{subfigure}[b]{0.18\linewidth}
		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_groundtruth.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.18\linewidth}
		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_normal_GCNN-GCNN.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.18\linewidth}
		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_normal_GCNN-CNN.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.18\linewidth}
		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_normal_GCNN-NOC.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.18\linewidth}
		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_normal_SVD.png}
	\end{subfigure}

	\begin{subfigure}[b]{0.18\linewidth}
		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_img.png}
		\caption{GT}
	\end{subfigure}
	\begin{subfigure}[b]{0.18\linewidth}
		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_error_GCNN-GCNN.png}
		\caption{GCNN}
	\end{subfigure}
	\begin{subfigure}[b]{0.18\linewidth}
		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_error_GCNN-CNN.png}
		\caption{CNN}
	\end{subfigure}
	\begin{subfigure}[b]{0.18\linewidth}
		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_error_GCNN-NOC.png}
		\caption{NOC}
	\end{subfigure}
	\begin{subfigure}[b]{0.18\linewidth}
		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_error_SVD.png}
		\caption{SVD}
	\end{subfigure}

@@

	\caption{Surface Normal Inference based GCNN model on "Dragon´´ object. The first row shows the estimated surface normal. The second row is the angle error map.}
	\label{fig:gcnn-eval}
\end{figure}

A qualitative evaluation on object "dragon" is shown in Figure \ref{fig:gcnn-eval}. SVD approach is considered as the baseline shown in last column. As shown in the figure, learning based methods performs better than SVD in terms of angle error. The SVD approach is failed to deal with semi-dense input since there exists many points that missing neighbors. The GCNN model is especially good at noise input due to the gated convolution layer design. As a further detailed comparison, \ref{fig:gcnn-eval-synthetic-zoom-in} gives a closer visualization on the same object.

%% fig:gcnn-eval-synthetic-zoom-in
\begin{figure}[H]
	\centering
	\begin{subfigure}[b]{0.18\linewidth}
		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_7_normal_GT.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.18\linewidth}
		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_7_normal_GCNN-GCNN.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.18\linewidth}
		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_7_normal_GCNN-NOC.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.18\linewidth}
		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_7_normal_GCNN-CNN.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.18\linewidth}
		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_7_normal_SVD.png}
	\end{subfigure}

	\begin{subfigure}[b]{0.18\linewidth}
		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_7_img.png}
		\caption{GT}
	\end{subfigure}
	\begin{subfigure}[b]{0.18\linewidth}
		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_7_error_GCNN-GCNN.png}
		\caption{GCNN}
	\end{subfigure}
	\begin{subfigure}[b]{0.18\linewidth}
		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_7_error_GCNN-NOC.png}
		\caption{NOC}
	\end{subfigure}
	\begin{subfigure}[b]{0.18\linewidth}
		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_7_error_GCNN-CNN.png}
		\caption{CNN}
	\end{subfigure}
	\begin{subfigure}[b]{0.18\linewidth}
		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_7_error_SVD.png}
		\caption{SVD}
	\end{subfigure}

	\caption{Zoom in of the center region of Dragon object. The first row is surface normal, the second row is the corresponding errors. NOC model has no skip connnection, CNN model replace gated convolution layer to standard convolution layer.}
	\label{fig:gcnn-eval-synthetic-zoom-in}
\end{figure}
As shown in figure \ref{fig:gcnn-eval-synthetic-zoom-in}, the GCNN method gives a sharper edge prediction on the horn area of the dragon object, as well as the scales, whereas the no skip version (NOC) is blurry in the same area.

The CNN version has the skip connection thus gives a better detail than NOC model. However, if we compare the error map of GCNN and CNN in figure \ref{fig:gcnn-eval}, the CNN has less accurate in the smooth area than GCNN model. Like the dragon body, CNN model has a overall higher error than GCNN. It is because the noise of the input still disturb the CNN model and it takes the input noise into account for normal estimation which deviate to the correct surface normal. When we look back to the GCNN based method, we can found that the surface normal has better performance in the smooth area compare to the CNN approach and a sharp detail compare to the no skip connection version.

Table \ref{tab:gcnn-eval} gives a quantitative evaluation for GCNN model. It bases on 100 different test scenes in the "synthetic-50-5´´ dataset with angle metrics for evaluation.

	\centering
	\begin{tabular}{l l l l l l }
		\tabhead{Model} & \tabhead{Angle} & \tabhead{Time /ms} & \tabhead{bz} & \tabhead{lr-schedule} & \tabhead{lr-df}\\
		SVD(baseline)  & 41.14  & 320.40 & 8 & 8,1000 & 0.5\\ 
		\hline
		GCNN  & 10.64  & 10.44 & 8 & 8,1000 & 0.5\\ 
		\hline
		GCNN-NOC & 13.61 & 5.38 & 8 & 8,1000 & 0.5\\
		\hline
		CNN & 15.35 & 4.15 & 8 & 8,1000 & 0.5\\
	\end{tabular}
	\caption{The performance of the GCNN model for geometry information based normal inference. The angle error is the average angle error of all valid pixels in the test case. bz stands for batch size, lr-schedule stands for learning rate schedule, lr-df stands for learning rate decay factor.}	
	\label{tab:gcnn-eval}
\end{table}

@@

For the approach using illuminated calibrated RGBD image, the task is undertaken by Trip-Net introduced in \ref{sec:trip-net}. 
The qualitative evaluation is shown in figure \ref{fig:trip-eval}. As a comparison, we placed GCNN result in the last column. The training settings for all the models are exact the same to ensure fairness. As shown in the figure, TripNet uses illuminated calibrated RGBD image has a better performance than GCNN model. The dragon scales are sharper in TripNet result. Figure \ref{fig:tripnet-eval-synthetic-zoom-in} gives a closer visualization.
%% TripNet-eval
\begin{figure}[H]
	\centering
	\begin{subfigure}[b]{0.18\linewidth}
		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_groundtruth.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.18\linewidth}
		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_normal_an2-8-1000.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.18\linewidth}
		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_normal_GCNN-GCNN.png}
	\end{subfigure}

>>>>

\section{Training Details}

The approaches are trained on dataset "synthetic-50-5" as mentioned in Chapter \ref{ch:04} with 3000 scenes. Each scene has a depth map with dimension $ 128\times 128 \times $ in height, width and channel, an image with dimension $ 128\times 128 \times 1 $.  The depth map is converted to 3D vertex map as introduced in Chapter \ref{ch:04}. The light map is calculated based on vertex map and the known light position. We create a tensor in PyTorch that includes vertex map, image and the light direction for each scene and considered it as one training case. Thus 3000 scenes has corresponding 3000 training cases. Each scene has a corresponding ground-truth normal map for loss calculation and the evaluation.

\begin{figure}[H]
	\centering

	\begin{subfigure}[b]{0.20\linewidth}
		\includegraphics[width=\linewidth]{./Figures/test_scenes/05051.depth0.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.20\linewidth}
		\includegraphics[width=\linewidth]{./Figures/test_scenes/05051.depth0_noise.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.20\linewidth}
		\includegraphics[width=\linewidth]{./Figures/test_scenes/05051.image0.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.20\linewidth}
		\includegraphics[width=\linewidth]{./Figures/test_scenes/05051.normal0.png}
	\end{subfigure}

	\begin{subfigure}[b]{0.20\linewidth}
		\includegraphics[width=\linewidth]{./Figures/test_scenes/03094.depth0.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.20\linewidth}
		\includegraphics[width=\linewidth]{./Figures/test_scenes/03094.depth0_noise.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.20\linewidth}
		\includegraphics[width=\linewidth]{./Figures/test_scenes/03094.image0.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.20\linewidth}
		\includegraphics[width=\linewidth]{./Figures/test_scenes/03094.normal0.png}
	\end{subfigure}

	\begin{subfigure}[b]{0.20\linewidth}
		\includegraphics[width=\linewidth]{./Figures/test_scenes/05111.depth0.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.20\linewidth}
		\includegraphics[width=\linewidth]{./Figures/test_scenes/05111.depth0_noise.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.20\linewidth}
		\includegraphics[width=\linewidth]{./Figures/test_scenes/05111.image0.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.20\linewidth}
		\includegraphics[width=\linewidth]{./Figures/test_scenes/05111.normal0.png}
	\end{subfigure}

	\begin{subfigure}[b]{0.20\linewidth}
		\includegraphics[width=\linewidth]{./Figures/test_scenes/05113.depth0.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.20\linewidth}
		\includegraphics[width=\linewidth]{./Figures/test_scenes/05113.depth0_noise.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.20\linewidth}
		\includegraphics[width=\linewidth]{./Figures/test_scenes/05113.image0.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.20\linewidth}
		\includegraphics[width=\linewidth]{./Figures/test_scenes/05113.normal0.png}
	\end{subfigure}

	\begin{subfigure}[b]{0.20\linewidth}
		\includegraphics[width=\linewidth]{./Figures/test_scenes/05126.depth0.png}
		\caption{Depth Map}
	\end{subfigure}
	\begin{subfigure}[b]{0.20\linewidth}
		\includegraphics[width=\linewidth]{./Figures/test_scenes/05126.depth0_noise.png}
		\caption{Add noise}
	\end{subfigure}
	\begin{subfigure}[b]{0.20\linewidth}
		\includegraphics[width=\linewidth]{./Figures/test_scenes/05126.image0.png}
		\caption{Image}
	\end{subfigure}
	\begin{subfigure}[b]{0.20\linewidth}
		\includegraphics[width=\linewidth]{./Figures/test_scenes/05126.normal0.png}
		\caption{Normal}
	\end{subfigure}

	\caption{Some of the test scenes during the training. From top to bottom, baoshanlu, Washington, Garfield, Dragon, Bus}
	\label{fig:test-scene}
\end{figure}

The training processes are evaluated in every epochs with 29 evaluation scenes that model never seen before, which contains the 5 different objects in the ``synthetic-50-5" test set. Figure \ref{fig:test-scene} shows some of the test scenes during the training work. Note that the position of objects are not placed naturally on the stage but with a random rotation in X, Y, Z axes, respectively.

The training pipeline use batch size $ 8 $,  Adam optimizer (\cite{adam}), learning rate start from  $ 1\times10^{-3} $, learning schedule [8,1000], learning decay factor 0.5. The model is trained with PyTorch 1.10.0a0, CUDA 11.4.1, GPU with single NVIDIA GEFORCE RTX 3090. It takes 14 hours to train GCNN and 35 hours to train the Trip-Net. We terminate the training when the evaluation on the test dataset converged.

\section{GCNN model based on Geometry Information}
The GCNN model is the base model of the whole thesis. The architecture is described in \ref{sec:gcnn}. We use a single GCNN to estimate the surface normal based on geometry information. It uses vertex map as input to estimate the corresponding tangent surface normal map.

In order to verify the applicability of UNet architecture and Gated Convolution layer for the normal inference task, two similar models are created. 
We replace all of the gated layer to standard convolution layers in the network but keeps all of the other settings same in model ``CNN". It is used to verify the performance the gated convolution layers. As mentioned in chapter \ref{ch:03}, the gated layer is designed to deal with noised input. Since all of the vertex map in the dataset has been added noise, the GCNN is supposed to over-perform ``CNN". Another model called ``NOC" is designed to verify the skip connection in the UNet, which simply removes the skip connections in the network but keeps other settings same. Is is designed to show the validation of skip connections. Figure \ref{fig:gcnn-training-history} shows the training history on BerHu Loss. The GCNN approach achieves a lower loss from start to the end of the training.

\begin{figure}[th]
	\centering
	\includegraphics[width=.45\textwidth]{./Figures/gcnn_training_loss.png}
	\includegraphics[width=.45\textwidth]{./Figures/gcnn_eval_loss.png}
	\caption{The training history of GCNN model. The line chart records the training BerHu loss of the model GCNN, NOC and CNN. The left shows the training loss history whereas the right one shows the evaluation loss history.}
	\label{fig:gcnn-training-history}
\end{figure}

\section{Trip-Net model based on Calibrated Illuminated RGB-D Image}
The Trip-Net model uses three times GCNN architecture with 4 times fusions, which is more difficult to train. It takes the calibrated illuminated RGB-D images as input to estimate the surface normal map. For the sake of comparison, we take the GCNN model as a baseline, to observe the beneficial of illuminated information using with Trip-Net architecture. Since it is more complicate than GCNN, we also explored the optimum fusion times of the Trip-Net to see any possibility for the model simplification. A set of similar models have been trained with same settings but different fusion times, denotes by Trip-Net-F$ x $F, where $ x $ denotes the fusion times. We evaluate the fusion times from 1 to 4. For the learning rate.  we set $ 1e-3 $. It goes well with GCNN model but lead to loss explosion in Trip-Net. Thus we set a learning rate schedule with an extra decay step at epoch 8. The decay factor is $ 0.5$. The batch size is chosen as 8.

Figure \ref{fig:trip-net-training-history} shows the training history of these models on BerHu Loss. As shown in the loss figure, all of the four models has a reasonable learning rate. Trip-Net with four times fusion converges faster than others and also achieve a lower loss. Trip-Net-F3F converges slower than Trip-Net but achieved to a similar evaluation loss. The evaluation loss in Trip-Net-F1F and Trip-Net-F2F are relative higher than 3 or 4 times fusions model.

\begin{figure}[th]
	\centering
	\includegraphics[width=.45\textwidth]{./Figures/gcnn_training_loss.png}
	\includegraphics[width=.45\textwidth]{./Figures/gcnn_eval_loss.png}
	\caption{The training history of Trip-Net model. The line chart records the training BerHu loss of the model Trip-Net, Trip-Net-F1, Trip-Net-F2, Trip-Net-F3, GCNN.}
	\label{fig:trip-net-training-history}
\end{figure}

However, the sacrifice of accuracy gives a relatively lighter model. Since we remove the fusions between different pipes, the corresponding upsampling layers in the image and light pipes can also be removed. The model can be trained faster and the size is reduced as well. Table \ref{tab:trip-net-size-compare} gives a comparison of the size and training time among different models.

	\centering
	\begin{tabular}{l l l l l l l }
		\tabhead{Model} & $ \# $\textbf{Total} &\textbf{ V-P} & \textbf{L-P} & \textbf{I-P} & \tabhead{Size /MB} & \tabhead{Time /h}\\
		Trip-Net-F1F  			& 88 &  40 & 24 & 24 & 106  &  9.82\\ 
		\hline
		Trip-Net-F2F 			& 92 & 40 & 26 & 26 & 137 &  7.35\\ 
		\hline
		Trip-Net-F3F 			& 96 & 40 & 28 & 28 & 167 &  7.35\\
		\hline
		Trip-Net 				& 100 & 40 & 30 & 30 & 198 & 9.15\\
		\hline
		GCNN 					& 32 & 32 & 0 & 0 & 46 & 2.18\\
	\end{tabular}
	\caption{Model information. Columns V-P, L-P and I-P represent the number of convolution layers in vertex pipe, light pipe and image pipe respectively. Note that one gated convolution layer is constructed with 2 standard layers, thus it is counted as 2. }	
	\label{tab:gcnn-eval-mean}
\end{table}

\section{Evaluation}

Based on metrics proposed by \cite{geometry_based_solution}, 6 different metrics are used for evaluation. Note that the input vertex map is only semi-dense. One of the benefit of GCNN architecture is the robust to the noisy input, thus in the evaluation, all the points including missing points in the input vertex map are taken into account.

\paragraph{Average Angle Error Metric}
The metric calculate the average angle error for each point between the inferred normal and ground-truth normal. 
\paragraph{Median Angle Error Metric}
The metric calculate the median angle error of all the point in the normal map.
\paragraph{5 Degree Error Metric}
The metric calculate the percentage of the predicted normals that has error less than 5 degrees comparing to ground-truth.
\paragraph{11.5 Degree Error Metric}
The metric calculate the percentage of the predicted normals that has error less than 11.5 degrees comparing to ground-truth.
\paragraph{22.5 Degree Error Metric}
The metric calculate the percentage of the predicted normals that has error less than 22.5 degrees comparing to ground-truth.
\paragraph{30 Degree Error Metric}
The metric calculate the percentage of the predicted normals that has error less than 30 degrees comparing to ground-truth.

We evaluate the trained models on ``synthetic-50-5". 5 objects are considered in the test dataset. They are: $ Baoshanlu $, $ Bus $, $ Dragon $, $ Garfield $, and $ Washington $. Each object has 20 scenes with total 100 scenes for 5 objects. The test objects do not exist in the training dataset. We evaluate all the presented models on the test dataset, in order to fit them in one table, the name of each models are simplified. $ SVD $ model use SVD optimization method, $ NOC $ model is the no skip connection version of $ GCNN $, $ CNN $ is the CNN version of $ GCNN $. $ F1 $, $ F2 $, $ F3 $,$ F4 $ means the fusion times in the Trip-Net.

Among all the columns, the most important models are $ GCNN $ (depth map based) and  $ F4 $ (calibrated illuminated RGB-D image based), which is the core result of this thesis. When evaluate the $ GCNN $ models, we can take $ SVD $ model as baseline, $ NOC $ and $ CNN $ are used to verify the performance of $ GCNN $ model. When evaluate the $ F1-F4 $ models, we can take $ GCNN $ model as baseline.

%% mean metric
\begin{table}[H]
	\centering
	\begin{tabular}{l l | l | l l l | l l l l }
		\tabhead{Object} & $ \# $ & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{NOC} & \tabhead{CNN} & \tabhead{F1}& \tabhead{F2}& \tabhead{F3}& \tabhead{F4}\\
		Baoshanlu  		& 20 & 35.66 & 11.09 & 13.58 & 15.55 & & & & 9.82 \\ 
		\hline
		Bus 			& 20 & 31.93 & 7.79 & 8.95 & 11.93 & & & & 7.32\\ 
		\hline
		Dragon 			& 20 & 39.57 & 10.60 & 15.29 & 16.03 & & & & 7.35 \\
		\hline
		Garfield 		& 20 & 39.69 & 10.20 & 12.50 & 14.46 & & & & 9.15 \\
		\hline
		Washington 		& 20 & 42.83 & 13.43 & 17.59 & 18.71 & & & & 12.13\\
	\end{tabular}
	\caption{Average Angle Error of the evaluation dataset.}	
	\label{tab:eval-mean}
\end{table}

%% median metric
\begin{table}[H]
	\centering
	\begin{tabular}{l l | l | l l l | l l l l }
		\tabhead{Object} & $ \# $ & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{NOC} & \tabhead{CNN} & \tabhead{F1}& \tabhead{F2}& \tabhead{F3}& \tabhead{F4}\\
		Baoshanlu  		& 20 & 34.06 & 8.86 & 10.82 & 13.25 & & & & 7.62 \\ 
		\hline
		Bus 			& 20 & 34.14 & 4.44 & 5.02 & 8.69 & & & & 4.01 \\ 
		\hline
		Dragon 			& 20 & 36.43 & 7.62 & 11.10 & 13.26 & & & & 5.06 \\
		\hline
		Garfield 		& 20 & 37.60 & 6.40 & 8.90 &11.31 & & & & 5.81\\
		\hline
		Washington 		& 20 & 36.89 & 7.64 & 11.38 & 13.64& & & & 6.76\\
	\end{tabular}
	\caption{Median Angle Error of the evaluation dataset.}	
	\label{tab:eval-median}
\end{table}

%% 5 degree metric
\begin{table}[H]
	\centering
	\begin{tabular}{l l | l | l l l |l l l l }
		\tabhead{Object} & $ \# $ & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{NOC} & \tabhead{CNN} & \tabhead{F1}& \tabhead{F2}& \tabhead{F3}& \tabhead{F4}\\
		Baoshanlu  		& 20 & 0.01 & 0.25 & 0.18 & 0.11 & & & & 0.31\\ 
		\hline
		Bus 			& 20 & 0.00 & 0.56 & 0.50 & 0.23 & & & & 0.59 \\ 
		\hline
		Dragon 			& 20 & 0.00 & 0.31 & 0.17 & 0.10 & & & & 0.50\\
		\hline
		Garfield 		& 20 & 0.00 & 0.41 & 0.27 & 0.14 & & & & 0.45\\
		\hline
		Washington 		& 20 & 0.00 & 0.38 & 0.26 & 0.10 & & & & 0.41\\
	\end{tabular}
	\caption{Percent of error less than 5 degree of the evaluation dataset.}	
	\label{tab:eval-5d}
\end{table}

%% 11.5 degree metric
\begin{table}[H]
	\centering
	\begin{tabular}{l l | l | l l l | l l l l }
		\tabhead{Object} & $ \# $ & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{NOC} & \tabhead{CNN} & \tabhead{F1}& \tabhead{F2}& \tabhead{F3}& \tabhead{F4}\\
		Baoshanlu  		& 20 & 0.03 & 0.62 & 0.52 & 0.41 & & & & 0.69\\ 
		\hline
		Bus 			& 20 & 0.05 & 0.81 & 0.78 & 0.65 & & & & 0.83 \\ 
		\hline
		Dragon 			& 20 & 0.02 & 0.69 & 0.51 & 0.40 & & & & 0.82\\
		\hline
		Garfield 		& 20 & 0.03 & 0.72 & 0.62 & 0.51 & & & & 0.75\\
		\hline
		Washington 		& 20 & 0.02 & 0.62 & 0.50 & 0.40 & & & & 0.66\\
	\end{tabular}
	\caption{Percent of error less than 11.5 degree of the evaluation dataset.}	
	\label{tab:eval-11d}
\end{table}

%% 22.5 degree metric
\begin{table}[H]
	\centering
	\begin{tabular}{l l | l | l l l | l l l l }
		\tabhead{Object} & $ \# $ & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{NOC} & \tabhead{CNN} & \tabhead{F1}& \tabhead{F2}& \tabhead{F3}& \tabhead{F4}\\
		Baoshanlu  		& 20 & 0.18 & 0.90 & 0.84 & 0.79 & & & & 0.92\\ 
		\hline
		Bus 			& 20 & 0.26 & 0.93 & 0.91 & 0.89 & & & & 0.94\\ 
		\hline
		Dragon 			& 20 & 0.14 & 0.90 & 0.79 & 0.80 & & & & 0.95\\
		\hline
		Garfield 		& 20 & 0.13 & 0.89 & 0.86 & 0.84 & & & & 0.91\\
		\hline
		Washington 		& 20 & 0.14 & 0.81 & 0.72 & 0.72 & & & & 0.84\\
	\end{tabular}
	\caption{Percent of error less than 22.5 degree of the evaluation dataset.}	
	\label{tab:eval-22d}
\end{table}

%% 30 degree metric
\begin{table}[H]
	\centering
	\begin{tabular}{l l | l | l l l | l l l l }
		\tabhead{Object} & $ \# $ & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{NOC} & \tabhead{CNN} & \tabhead{F1}& \tabhead{F2}& \tabhead{F3}& \tabhead{F4}\\
		Baoshanlu  		& 20 & 0.37 & 0.96 & 0.93 & 0.90 & & & & 0.97 \\ 
		\hline
		Bus 			& 20 & 0.43 & 0.96 & 0.94 & 0.93 & & & & 0.96 \\ 
		\hline
		Dragon 			& 20 & 0.30 & 0.95 & 0.88 & 0.90 & & & & 0.98 \\
		\hline
		Garfield 		& 20 & 0.27 & 0.94 & 0.92 & 0.91 & & & & 0.95 \\
		\hline
		Washington 		& 20 & 0.28 & 0.88 & 0.81 & 0.82 & & & & 0.90\\
	\end{tabular}
	\caption{Percent of error less than 30 degree of the evaluation dataset.}	
	\label{tab:eval-30d}
\end{table}

\section{Visualization evaluation on GCNN model}
A qualitative evaluation on object "dragon" is shown in Figure \ref{fig:gcnn-eval}. As shown in the figure, GCNN model achieved a mean angle error in 9 degrees on this dragon object. The image has an overall good performance on the whole object. A closer evaluation is shown in Figure \ref{fig:gcnn-eval-synthetic-zoom-in}, the normal accuracy especially good on the smooth surface, like the body area. In the same case, NOC model as shown in Figure  \ref{fig:gcnn-eval-multi-model} has a overall worse normal than GCNN model in the smooth area. CNN model keeps the skip connection thus gives a sharper result than NOC model, however, the overall smooth part of the model is still worse than GCNN. Besides, the sharp area like the hindleg, the head of dragon object, CNN model gives a much brighter error map (which lead to a higher angle error).

%% GCNN-eval
\begin{figure}[H]
	\centering
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_img.png}
		\caption{Image}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_groundtruth.png}
		\caption{GT}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_normal_GCNN-GCNN.png}
		\caption{Predict}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_error_GCNN-GCNN.png}
		\caption{Error}
	\end{subfigure}

@@

	\caption{Normal inference based on GCNN. Test image has resolution $ 128\times128 $}
	\label{fig:gcnn-eval}
\end{figure}

%% GCNN zoom in eval
\begin{figure}[H]
	\centering
	\begin{subfigure}[b]{0.18\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/eval_7_22_-8_normal.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.18\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/eval_7_2_22_normal.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.18\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/eval_7_32_12_normal.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.18\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/eval_7_42_-28_normal.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.18\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/eval_7_12_-48_normal.png}
	\end{subfigure}

	\begin{subfigure}[b]{0.18\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/eval_7_22_-8_error.png}
		\caption{Scale}
	\end{subfigure}
	\begin{subfigure}[b]{0.18\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/eval_7_2_22_error.png}
		\caption{Head}
	\end{subfigure}
	\begin{subfigure}[b]{0.18\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/eval_7_32_12_error.png}
		\caption{Foreleg}
	\end{subfigure}
	\begin{subfigure}[b]{0.18\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/eval_7_42_-28_error.png}
		\caption{Hindleg}
	\end{subfigure}
	\begin{subfigure}[b]{0.18\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/eval_7_12_-48_error.png}
		\caption{Tail}
	\end{subfigure}

	\caption{Zoom in of some regions of Dragon object. The first row is surface normal, the second row is the corresponding errors. Zoom-in normal map corresponding $ 32\times32 $ points in the original matrix.}
	\label{fig:gcnn-eval-synthetic-zoom-in}
\end{figure}

%% compare to other models

%% GCNN zoom in eval
\begin{figure}[H]
	\centering
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_groundtruth.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_normal_GCNN-GCNN.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_normal_GCNN-NOC.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_normal_GCNN-CNN.png}
	\end{subfigure}

	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_img.png}
		\caption{GT}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_error_GCNN-GCNN.png}
		\caption{GCNN}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_error_GCNN-NOC.png}
		\caption{NOC}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_error_GCNN-CNN.png}
		\caption{CNN}
	\end{subfigure}

	\caption{Comparison of GCNN model with no skip connection version(NOC) and standard convolution layer only version (CNN). The second row is the corresponding mean average degree error.}
	\label{fig:gcnn-eval-multi-model}
\end{figure}

@@

For the approach using illuminated calibrated RGBD image, the task is undertaken by Trip-Net introduced in \ref{sec:trip-net}. 
The qualitative evaluation is shown in figure \ref{fig:trip-eval}. In order to show the effectiveness of added illuminated information, the training settings for all the models are exact the same. We also use the same input as we did in GCNN evaluation. The error of Trip-Net is 6 degree whereas the GCNN is 9.

As shown in the figure \ref{fig:tripnet-eval-synthetic-zoom-in}, the scale on the dragon body is much easier to detect and close to the ground-truth. The head region gives a sharper edge prediction. All of the five sampled zoom-in regions in the Trip-Net has a better performance than GCNN.

%% TripNet-eval
\begin{figure}[H]
	\centering
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_img.png}
		\caption{Image}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_groundtruth.png}
		\caption{GT}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_normal_an2-8-1000.png}
		\caption{Predict}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_error_an2-8-1000.png}
		\caption{Error}
	\end{subfigure}
